Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-18 paper/paper.tex
Update Overleaf

@@

Importance of working in low-resource languages and with scarse training data,
to encourage transfer learning, unsupervised learning, and low cost solutions

>>>>

The accelerated growth of the Internet and the increased production of textual resources in all areas of human endeavour has created both new opportunities and new challenges for the research community.
On one hand, larger datasets can be collected and used to build increasingly powerful machine learning models~(e.g., GPT-3 and related).
On the other hand, is becoming increasingly difficult to organise, categorise, cross-reference, and fact-check the textual information available online.
The ease of access to both publication and consumption of textual information is also one of the causes of the increasingly worrying phenomena of fake news.

@@

Importance of working in low-resource languages and with scarce training data,
to encourage transfer learning, unsupervised learning, and low cost solutions
